Manual of comparing optimal subsampling with model robust optimal subsampling method for logistic regression (exponential distribution)

### 2023-03-05 Manual.Rmd
Manual updated after removing Classical

### 2.2.1 Classical/R_Scripts

@@

* Data stored in **Generate_Big_Data** is transferred to **Classical/Analysis**.

@@

## 2.2.2 Classical/Analysis

@@

* **Summary_Rmarkdown.R** in the **Rmarkdown/Classical/Summary** folder compares the sub-sampling methods through Mean Squared Error, variance and model information through the **Best_Subsampling_Method.Rmd**.

@@

### 2.6.1 Summary/Classical/Model_[1 or 2 or 3 or 4]/Data/Efficiency

@@

* Using these data files only summarising through the files in **Rmarkdown/Classical/Summary** occurs.

@@

* Use **Articles.Rmd** to generate plots relevant to the paper as pdf files **SMSE_MI_LR_TV_Exp_mMSE.pdf** and **SMSE_MI_LR_TV_Exp_mVc.pdf**.

>>>>

### 2.2.1 R_Scripts

@@

* Data stored in **Generate_Big_Data** is transferred to **Analysis**.

@@

## 2.2.2 Analysis

@@

* **Summary_Rmarkdown.R** in the **Rmarkdown/Summary** folder compares the sub-sampling methods through Mean Squared Error, variance and model information through the **Best_Subsampling_Method.Rmd**.

@@

### 2.6.1 Summary/Model_[1 or 2 or 3 or 4]/Data/Efficiency

@@

* Using these data files only summarising through the files in **Rmarkdown/Summary** occurs.

@@

* Use **Articles.Rmd** to generate plots relevant to the paper as pdf files **Artilce_Plots/SMSE_MI_LR_TV_Exp_mMSE.pdf** and **Artilce_Plots/SMSE_MI_LR_TV_Exp_mVc.pdf**.
